---
title: "Presentation"
subtitle: "Assignment: Developing Data Products" 
author: "Ellen Bayens"
date: "15-12-2019"
output: ioslides_presentation
widescreen: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{css, echo = FALSE}
.remark-slide-content {
  font-size: 28px;
  padding: 20px 80px 20px 80px;
}
.remark-code, .remark-inline-code {
  background: #f0f0f0;
}
.remark-code {
  font-size: 24px;
}
.huge .remark-code { /*Change made here*/
  font-size: 200% !important;
}
.tiny .remark-code { /*Change made here*/
  font-size: 50% !important;
}
```


## Explanation on the shiny app 

I made an shiny app with an overview of dutch universities and its number of students. You can find the app here: 

* <https://corhelene.shinyapps.io/Assignment94/>.

This app shows you the number of students on Dutch universities.
With the checkboxes you can choose whether you want to see only the fulltime students, or also the parttime students.

Here is the link to the code in github: 

* [ui.R](https://github.com/Corhelene/Assignment94/blob/master/Assignment94/ui.R)
* [server.R](https://github.com/Corhelene/Assignment94/blob/master/Assignment94/server.R)



## The code used for the shiny app {.smaller}

```{r message = FALSE, echo = TRUE}
library(readxl); library(dplyr); library(plotly)
# Loading the data
fileURL <- "https://www.duo.nl/open_onderwijsdata/images/02-ingeschrevenen-wo-naar-opleidingsvorm-2018.xlsx"
download.file(fileURL,destfile = "data.xlsx",mode = "wb")
mydata <- read_excel("data.xlsx")
names(mydata) <- gsub(" ", "_", names(mydata))

#Prepare data for plot numbers of students per city
mydata1 <- mydata %>%
    filter(!is.na(BEVOEGD_GEZAG_NUMMER)) %>%
    group_by(PLAATSNAAM) %>%
    summarize(voltijd = sum(VOLTIJD_ONDERWIJS),deeltijd = sum(DEELTIJD_ONDERWIJS), count = n()) %>%
    mutate(combined = voltijd + deeltijd) %>%
    arrange(desc(voltijd))
mydata1$PLAATSNAAM <- factor(mydata1$PLAATSNAAM, levels = c(as.character(mydata1$PLAATSNAAM)))

#Make the plots for number of studens per city
p_vol_deel <- plot_ly(x=mydata1$PLAATSNAAM, y=mydata1$voltijd, type = "bar", name = "Fulltime + Parttime") %>%
    add_trace(y = mydata1$deeltijd, name = "Parttime") %>%
         layout(annotations = list(x = 0.2 , y = 1.05, text = "Number of students (fulltime/parttime) per city", 
                                   showarrow = F, xref='paper', yref='paper'), showlegend = FALSE)
p_vol <- plot_ly(x=mydata1$PLAATSNAAM, y=mydata1$voltijd, type = "bar", name = "Fulltime") %>%
    layout(title = "Number of fulltime students per city", yaxis = list(title = 'Amount'), 
          xaxis = list(title = "City"), barmode = 'stack')       
```


## The code used for the shiny app (2nd part) {.smaller}

```{r message = FALSE, echo = TRUE}
#Prepare data for number of students per specialization
mydata3 <- mydata %>%
    filter(!is.na(BEVOEGD_GEZAG_NUMMER)) %>%
    group_by(CROHO_ONDERDEEL) %>%
    summarize(voltijd = sum(VOLTIJD_ONDERWIJS),deeltijd = sum(DEELTIJD_ONDERWIJS), count = n()) %>%
    mutate(combined = voltijd + deeltijd) %>%
    arrange(desc(voltijd))
mydata3$CROHO_ONDERDEEL <- factor(mydata3$CROHO_ONDERDEEL, levels = c(as.character(mydata3$CROHO_ONDERDEEL)))

#Make the plots for number of students per specialization
p2_vol_deel <- plot_ly(x=mydata3$CROHO_ONDERDEEL, y=mydata3$voltijd, type = "bar", name = "Fulltime + Parttime") %>%
    add_trace(y = mydata3$deeltijd, name = "Parttime") %>%
    layout(annotations = list(x = 1 , y = 1.05, text = "Number of students (fulltime/parttime) per specialization", showarrow = F, xref='paper', yref='paper'),showlegend = TRUE, barmode = 'stack')
p2_vol <- plot_ly(x=mydata3$CROHO_ONDERDEEL, y=mydata3$voltijd, type = "bar", name = "Voltijd") %>%
    layout(title = "Number of fulltime students per specialization", 
           yaxis = list(title = "Amount"), 
           xaxis = list(title = "City"), 
           barmode = 'stack')



```
## Results


```{r, fig.width=10, echo = TRUE}
subplot(p_vol_deel, p2_vol_deel)
```



